\documentstyle[12pt]{article}

\begin{document}

\section*{MICOM Meshmaps}

The following figures show the default relative position of the u, v and p 
staggered grids in the C-grid scheme used by the MICOM ocean model.  
They also show how grid points are numbered within two-dimensional arrays 
in the model.  
The size of the mesh array is chosen to just cover the model region, but 
because the array is rectangular a large fraction of the array might 
represent ``land'' for some regions.
In this case the region is a simple rectangle  $11 \Delta x$ (latitude) 
by $12 \Delta y$ (longitude) so all mesh array are dimensioned 11 by 12 
(i.e. idm=11 and jdm=12) and none of the array is ``land''.   
The figure has the standard map orientation (north at the top), but 
note that the first array dimension, i, is North to South and the second, 
j, is West to East.
The (West and East) sides of the region are on the v grid, at j=1 and 
j=12, and the top and bottom (north and south) are on the u grid at i=1 
and i=11.  
On the p grid all the nodes in row j=12 and in column i=11 are outside 
the region.  They are never used by the model, but would be set to zero 
in the topography array to indicate that they are over land.  
All other nodes in the topography array would have positive values 
representing the ocean depth at that point.
On the v grid all nodes in column i=11 are outside the region and are 
never used.  
Similarly, on the u grid all nodes in row j=12 are outside the region and 
are never used.
The u velocity component is southward and the v component is eastward.

\pagebreak
{\tt
\begin{verbatim}
                     MICOM U-V-P STAGGERED GRID.

                        IDM = 11 and JDM = 12

                                NORTH

       1     u---u---u---u---u---u---u---u---u---u---u   u
   1       v P v P v P v P v P v P v P v P v P v P v P v P
       2   | u   u   u   u   u   u   u   u   u   u   u | u
   2       v P v P v P v P v P v P v P v P v P v P v P v P
       3   | u   u   u   u   u   u   u   u   u   u   u | u
   3       v P v P v P v P v P v P v P v P v P v P v P v P
       4   | u   u   u   u   u   u   u   u   u   u   u | u
   4       v P v P v P v P v P v P v P v P v P v P v P v P
       5   | u   u   u   u   u   u   u   u   u   u   u | u
W  5       v P v P v P v P v P v P v P v P v P v P v P v P  E
E      6   | u   u   u   u   u   u   u   u   u   u   u | u  A
S  6       v P v P v P v P v P v P v P v P v P v P v P v P  S
T      7   | u   u   u   u   u   u   u   u   u   u   u | u  T
   7       v P v P v P v P v P v P v P v P v P v P v P v P
       8   | u   u   u   u   u   u   u   u   u   u   u | u
   8       v P v P v P v P v P v P v P v P v P v P v P v P
       9   | u   u   u   u   u   u   u   u   u   u   u | u
   9       v P v P v P v P v P v P v P v P v P v P v P v P
      10   | u   u   u   u   u   u   u   u   u   u   u | u
  10       v P v P v P v P v P v P v P v P v P v P v P v P
      11     u---u---u---u---u---u---u---u---u---u---u   u
  11       v P v P v P v P v P v P v P v P v P v P v P v P
 
           1   2   3   4   5   6   7   8   9   0   1   2
             1   2   3   4   5   6   7   8   9   0   1   2

                                SOUTH

I=1 to 11 is North to South, and u is southward velocity
J=1 to 12 is West  to East,  and v is  eastward velocity
\end{verbatim}
}

\end{document}
