\documentstyle[12pt]{article}

\begin{document}

\section*{HYCOM Meshmaps}

The following figures show the default relative position of the u, v and p 
staggered grids in the C-grid scheme used by the HYCOM ocean model.  
They also show how grid points are numbered within two-dimensional arrays 
in the model.  
The size of the mesh array is chosen to just cover the model region, but 
because the array is rectangular a large fraction of the array might 
represent ``land'' for some regions.  
In this case the region is a simple rectangle  $12 \Delta x$ (longitude) 
by $11 \Delta y$ (latitude) so all mesh array are dimensioned 12 by 11 
(i.e. idm=12 and jdm=11) and none of the array is ``land''. 
The figure has the standard map orientation (north at the top), and
the array orientation is also conventional with the first array dimension, 
i, West to East and the second, j, South to North.
The (West and East) sides of the region are on the u grid, at i=1 and 
i=12, and the bottom and top (south and north) are on the v grid at j=1 
and j=11.  
On the p grid all the nodes in row j=11 and in column i=12 are outside 
the region.  They are never used by the model, but would be set to zero 
in the topography array to indicate that they are over land.  
All other nodes in the topography array would have positive values 
representing the ocean depth at that point.
On the v grid all nodes in column i=12 are outside the region and are never
used.  
Similarly, on the u grid all nodes in row j=11 are outside the region and 
are never used.
The v velocity component is northward and the u component is eastward.

\pagebreak
{\tt
\begin{verbatim}
                     HYCOM U-V-P STAGGERED GRID.

                        IDM = 12 and JDM = 11

                                NORTH

  11       u P u P u P u P u P u P u P u P u P u P u P u P
      11     v---v---v---v---v---v---v---v---v---v---v   v
  10       u P u P u P u P u P u P u P u P u P u P u P u P
      10   | v   v   v   v   v   v   v   v   v   v   v | v
   9       u P u P u P u P u P u P u P u P u P u P u P u P
       9   | v   v   v   v   v   v   v   v   v   v   v | v
   8       u P u P u P u P u P u P u P u P u P u P u P u P
       8   | v   v   v   v   v   v   v   v   v   v   v | v
   7       u P u P u P u P u P u P u P u P u P u P u P u P
       7   | v   v   v   v   v   v   v   v   v   v   v | v
W  6       u P u P u P u P u P u P u P u P u P u P u P u P  E
E      6   | v   v   v   v   v   v   v   v   v   v   v | v  A
S  5       u P u P u P u P u P u P u P u P u P u P u P u P  S
T      5   | v   v   v   v   v   v   v   v   v   v   v | v  T
   4       u P u P u P u P u P u P u P u P u P u P u P u P
       4   | v   v   v   v   v   v   v   v   v   v   v | v
   3       u P u P u P u P u P u P u P u P u P u P u P u P
       3   | v   v   v   v   v   v   v   v   v   v   v | v
   2       u P u P u P u P u P u P u P u P u P u P u P u P
       2   | v   v   v   v   v   v   v   v   v   v   v | v
   1       u P u P u P u P u P u P u P u P u P u P u P u P
       1     v---v---v---v---v---v---v---v---v---v---v   v
 
           1   2   3   4   5   6   7   8   9   0   1   2
             1   2   3   4   5   6   7   8   9   0   1   2

                                SOUTH

I=1 to 12 is West  to East,  and u is  eastward velocity
J=1 to 11 is South to North, and v is northward velocity
\end{verbatim}
}

\end{document}
